---
title: "MovieLens - Case Study2"
author: "Siva Devarakonda"
date: "May 25, 2015"
output: slidy_presentation
---

## Case Study 2: Movie Lens Data Visualization
- Summary Statistics
- Histograms
- Correlation Study

## Slide with R Code and Output
```{r}
#Packages to include
library(RCurl)
library(ggplot2)
library(dplyr)
library(ggvis)
```

## Initialization of Datasets
## Part 1:
```{r}
d1 = getURL("https://raw.githubusercontent.com/dnchari/DS501_MovieLens/master/Results/unifiedMLDataMulti.csv")
mlMultiData = read.csv(text=d1)
summary(mlMultiData)
levels(mlMultiData$occupation)
levels(mlMultiData$genre)
# Movies with ratings > 4.5
nrow(filter(mlMultiData, rating > 4.5))
nrow(filter(mlMultiData, rating > 4.5 & gender == c("M")))
nrow(filter(mlMultiData, rating > 4.5 & gender == c("F")))

# Movies with median rating of 4.5 by Men
by_movie_title <- filter(mlMultiData, gender == c("M"))
by_movie_title <- group_by(by_movie_title, movie_title)
median_rating <- summarise(by_movie_title, count = n(), medrating = median(rating), meanrating = mean(rating))
ml_median_rating <- filter(median_rating, medrating > 4.5, count > 100)
ml_mean_rating <- filter(median_rating, meanrating > 4.5)

# Movies with median rating of 4.5 by Women
by_movie_title <- filter(mlMultiData, gender == c("F"))
by_movie_title <- group_by(by_movie_title, movie_title)
median_rating <- summarise(by_movie_title, count = n(), medrating = median(rating))
median_rating <- filter(median_rating, medrating > 4.5, count > 100)
nrow(median_rating)
```

## Part 2:
## Movie Rating By Genre

```{r}
qplot(rating, data = mlMultiData, fill = genre)
# Do not want to see it stacked
qplot(rating, data = mlMultiData, fill = genre, position = "dodge")
# Overall Movie Rating by Gender
qplot(rating, data = mlMultiData, fill = gender, position = "dodge")
qplot(rating, data = mlMultiData, facets = . ~ genre)
```

## Plot Histograms
## Histogram of ratings each movie received

```{r}
# 2.1 Histogram of number of ratings of all movies
qplot(rating, data=mlMultiData, geom="histogram")
```

#2.2 Histogram of number of ratings each movie received
{r}
dat <- summarise(group_by(mlMultiData, movie_title), count = n())
b <- ggplot(dat, aes(count))
b <- b + xlab("Movies") + ylab("Ratings Counts")
b <- b + geom_bar()
```

```{r}
# 2.3 Histogram of average number of ratings
mean_rating <- summarise(group_by(mlMultiData, movie_title), count = n(), meanrat = mean(rating))
b <- ggplot(mean_rating, aes(meanrat))
b <- b + xlab("Ratings")
b <- b + geom_bar()

# 2.4 Histogram of average rating for movies which are rated more than a 100 times
by_movie <- group_by(mlMultiData, movie_title)
by_movie <- summarise(by_movie, mean(rating), counts=n())
by_movie <- filter(by_movie, counts>100)
colnames(by_movie)<-c("movie_title", "av_rating", "counts")
a <- ggplot(by_movie, aes(av_rating))
a + geom_histogram()
a + geom_histogram(aes(fill = ..count..)) + scale_fill_gradient("Count", low = "red", high = "green")

# Average rating by occupation
by_occ <- group_by(mlMultiData, occupation)
by_occ <- summarise(by_occ, mean(rating), median(rating), counts=n())
colnames(by_occ) <- c("occupation", "mean_rating", "median_rating", "counts")

by_occ %>% 
  ggvis(~occupation, ~counts, fill := 'green') %>%
  layer_bars(width = 10) %>%
  set_options(height = 300, width = 400)
```

# Correlation: Men vs. Women
# Scatter plot of men vs. women and their mean rating for every movie
```{r}
by_movie <- group_by(mlMultiData, movie_title)
by_f <- filter(by_movie, gender == c("F"))
by_f <- summarise(by_f, av_f = mean(rating))
by_m <- filter(by_movie, gender == c("M"))
by_m <- summarise(by_m, av_m = mean(rating))
combined <- merge(by_m, by_f,by =c("movie_title") )

ggplot(combined, aes(x=av_f, y=av_m)) +
    geom_point(shape=1)      # Use hollow circles

ggplot(combined, aes(x=av_f, y=av_m)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm)   # Add linear regression line 
                             #  (by default includes 95% confidence region)

ggplot(combined, aes(x=av_f, y=av_m)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region

ggplot(combined, aes(x=av_f, y=av_m)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
```
# Scatter plot of men vs. women and their mean rating for rating count > 200

```{r}
by_movie <- group_by(mlMultiData, movie_title)
by_f <- filter(by_movie, gender == c("F"))
by_f <- summarise(by_f, av_f = mean(rating), counts = n())
by_f <- filter(by_f, counts > 200)
by_f["gender"] = c("F")
by_m <- filter(by_movie, gender == c("M"))
by_m <- summarise(by_m, av_m = mean(rating), counts = n())
by_m <- filter(by_m, counts > 200)
by_m["gender"] = c("M")
combined <- merge(by_m, by_f,by =c("movie_title") )

# Extend the regression lines beyond the domain of the data
ggplot(combined, aes(x=av_f, y=av_m)) + geom_point(shape=1) + 
    scale_colour_hue(l=50) + # Use a slightly darker palette than normal
    geom_smooth(method=lm,   # Add linear regression lines
                se=FALSE,    # Don't add shaded confidence region
                fullrange=TRUE) # Extend regression lines

```